%\title{emnlp 2017 instructions}
% File emnlp2017.tex
%

\documentclass[11pt,letterpaper]{article}
\usepackage{emnlp2017}
\usepackage{times}
\usepackage{latexsym}
\usepackage{todonotes}
\usepackage{url}
\usepackage{blindtext}
\usepackage{fancybox, graphicx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{arydshln}
\usepackage{pgf-pie}
\usepackage{float}

% Uncomment this line for the final submission:
%\emnlpfinalcopy

%  Enter the EMNLP Paper ID here:
\def\emnlppaperid{388}

% To expand the titlebox for more authors, uncomment
% below and set accordingly.
% \addtolength\titlebox{.5in}    

\newcommand\BibTeX{B{\sc ib}\TeX}

\input{commands}
\title{Supervised Open Information Extraction}

% Author information can be set in various styles:
% For several authors from the same institution:
% \author{Author 1 \and ... \and Author n \\
%         Address line \\ ... \\ Address line}
% if the names do not fit well on one line use
%         Author 1 \\ {\bf Author 2} \\ ... \\ {\bf Author n} \\
% For authors from different institutions:
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \And  ... \And
%         Author n \\ Address line \\ ... \\ Address line}
% To start a seperate ``row'' of authors use \AND, as in
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \AND
%         Author 2 \\ Address line \\ ... \\ Address line \And
%         Author 3 \\ Address line \\ ... \\ Address line}
% If the title and author information does not fit in the area allocated,
% place \setlength\titlebox{<new height>} right after
% at the top, where <new height> can be something larger than 2.25in
\author{Siddharth Patwardhan \and Preethi Raghavan \\
  {\tt publication@emnlp2017.net}}

\date{}

\begin{document}

\maketitle

\begin{abstract}
  Open Information Extraction (Open IE) has gained popularity as an underlying representation in a
  wide array of semantic applications.
  However, the lack of a large gold standard corpus for Open IE has
  limited the development of automatic extraction techniques to largely rule-based algorithms.
  In a recent advancement, a first large Open IE corpus for verbal predicates was presented, which ``opens the door'' for applying modern machine learning techniques for this task.
  In this paper, we utilize this corpus to develop a first supervised Open IE extractor.
  As this is the first supervised Open IE system,
  we use a deep bi-LSTM transducer, proven to be useful in similar tasks, and focus on laying the basic building blocks needed for supervised Open IE: encoding, decoding, confidence estimation, and proper error analysis.
  Our evaluation shows that the new extractor significantly outperforms
  the currently most prominent Open IE systems.
\end{abstract}

\section{Introduction}
\label{sec:introduction}
\input{introduction}


\section{Background: Open Information Extraction}
\label{sec:background}
\input{background}



\section{Model}
\label{sec:model}
\input{model}

\section{Evaluation}
\label{sec:evaluation}
\input{evaluation}

\section{Related Work}
\label{sec:related}
\input{related}

\section{Conclusions and Future Work}
\label{sec:conclusions}
We presented the first supervised model for Open IE,
which uses of the recently published large scale corpus for the task \cite{Stanovsky2016EMNLP}.
We model the task as a word-transducing problem, and presented solutions and
adjustments for various task-specific challenges: the encoding-decoding of Open IE instances, while providing a relabeling scheme which alleviates an inherent label-bias, a metric for computing the confidence of an extraction,
and applied a bi-LSTM transducer which follows state-of-the-art models for supervised SRL.
We tested this model against very strong baselines consisting of the current top performing Open IE systems, and
found that it is superior in terms of overall aggregated precision and recall.
In future work, we plan to extend this model to include a more principled learning of the confidence metric,
as well as to extend it beyond non-verbal predicates, which first require supporting supervised
data sets for non-verbal Open IE.
\bibliography{bib}
\bibliographystyle{emnlp_natbib}

\end{document}
